Visualization of [fulle name] Fractional Integrals

### 2019-03-26 fractional/CMJ style files/article-template.tex
added a paragraph to introduction

\begin{biog} %comment out in initial submission to allow for double blind reviewing
\item[\biogpic{\includegraphics[width=84pt]{Woodrow_Wilson.pdf}}Woodrow Wilson] (twwilson@princeton.edu) received his PhD in history and political science from Johns Hopkins University. He held visiting positions at Cornell and Wesleyan before joining the faculty at Princeton, where he was eventually appointed president of the university.  Among his proudest accomplishments was the abolition of eating clubs at Princeton on the grounds that they were elitist.

\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
\end{biog}

It can be argued that fractional calculus is as old as classical calculus itself. Leibniz, who is regarded by many as the farther of calculs, invented the following notation: $\frac{d^n f(x)}{d^n x}$ Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he is responding to a question L'Hospital posed. L'Hospital asked the question: ``What if $n$ be a $\frac{1}{2}$?''. Liouville and Riemann laid much of the groundwork which was 
needed to define the Riemann-Liouville fractional integral [Laurent’].

>>>>

%\begin{biog} %comment out in initial submission to allow for double blind reviewing
%\item[\biogpic{\includegraphics[width=84pt]{Woodrow_Wilson.pdf}}Woodrow Wilson] (twwilson@princeton.edu) received his PhD in history and political science from Johns Hopkins University. He held visiting positions at Cornell and Wesleyan before joining the faculty at Princeton, where he was eventually appointed president of the university.  Among his proudest accomplishments was the abolition of eating clubs at Princeton on the grounds that they were elitist.

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}

The idea of integer-order differentiation and integration is well known to most undergraduates. However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e. fractional-order calculus).
Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. The reason fractional calsulus is not generally 
taught at the undegraduate level is partly due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. This paper 
is specifically written for undergraduate lecturers and is very pedigogical in nature. The aim of the paper is to motivate and enable undergraduate 
lectures to introduce undergraduate students to this fascinating mathematical discipline.

This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.

It can be argued that fractional-order calculus is as old as classical calculus itself. Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$. Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he is responding to a question L'Hospital posed. L'Hospital asked the question: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.'' Liouville and Riemann laid much of the groundwork which was needed to define the Riemann-Liouville fractional integral [Laurent’].
